Extreme heterogeneity of influenza virus infection in single cells

### 2018-01-16 paper/paper.tex
A few small tweaks to legends for new supplementary figures. Primary change is to better explain the dual staining strategy for HA / NS1

\figsupp[Synchronization of infection does not greatly affect heterogeneity. \label{figsupp:synchronize}]
{Flow cytometry analysis of expression of viral proteins in cells infected at an MOI of 0.1 (unsynchronized) or 0.2 (synchronized) as calculated by TCID50 on MDCK-SIAT1 cells. 
The higher MOI for synchronized infections was to attempt to account for loss of virus in washing steps.
Infections were synchronized by pre-adsorbing virus at 4$^{\circ}$C for 1h prior to initiation of infection by shifting temperature to 37$^{\circ}$C using pre-warmed media.
Cells were concurrently stained for HA and NS1 proteins 10 hours post initiation of infection.
Synchronization resulted in a small decrease in variability, particularly in intermediately-stained cells, but not a massive shift in distribution. 
Replicates shown.
}{\includegraphics[width=\linewidth]{figures/synchronize.jpg}}

\figsupp[Effects of infectious dose or coinfection state. \label{figsupp:flowdose}]
{
{\bf (A)}
Flow cytometry analysis of expression of viral proteins in cells infected at high (MOI 5 as calculated by TCID50 on MDCK-SIAT1 cells) or low (MOI 0.1) initial infectious dose.
Cells were concurrently stained for HA and NS1 proteins 10 hours post infection.
HA staining was analyzed in cells positive for NS1 (left), and NS1 staining was analyzed in cells positive for HA (right).
While a higher dose leads to more cells expressing high amounts of viral protein, it does not greatly increase the amount of viral protein in either the low-expressing or high-expressing cells. 
Therefore, higher viral dose does not lead to a large continuous increase in viral protein production among all cells -- rather, it mostly changes the proportions of cells that fall in different parts of the highly heterogeneous distribution.
{\bf (B)}
Cells were co-infected with a mix of wild-type virus and pseudovirus in which the HA gene was replaced by GFP flanked by the terminal regions of the HA gene segment at an MOI of 0.1 for each virus. 
At 10 hours post-infection, cells were stained for NS1 and HA expression and analyzed by flow cytometry for these proteins and GFP.
Cells could be annotated as infected by virions of the same type (wild-type infection indicated by presence of HA, or pseudovirus infection indicated by the presence of GFP) or both types of virions (indicated by presence of HA and GFP).
Coinfected cells, like cells infected at a higher infectious dose, occupy different positions in the distribution of viral protein production but do not not exhibit a continuous increase in viral protein production.
Replicates shown.
}{\includegraphics[width=\linewidth]{figures/Coinf.jpg}}
\end{figure}

@@

\figsupp[Pre-treating to reduce oxidative stress decreases the fraction of infected cells expressing detectable viral protein. \label{figsupp:oxidative}]
{Cells were treated as indicated with 15 mM N-acetylcysteine (NAC), an antioxidant, and infected at an MOI of 0.1 as calculated by TCID50 on MDCK-SIAT1 cells. 
At 10 hours post-infection, cells were analyzed by flow cytometry for HA expression.
Percentage HA-positive cells and gating shown.
Replicates shown.
}{\includegraphics[width=0.7\linewidth]{figures/antiox.jpg}}

>>>>

\figsupp[Synchronization of infection does not greatly affect heterogeneity. \label{figsupp:synchronize}]
{Flow cytometry analysis of expression of viral proteins in cells infected at an MOI of 0.1 (unsynchronized) or 0.2 (synchronized) as calculated by TCID50 on MDCK-SIAT1 cells. 
The higher MOI for synchronized infections was to attempt to account for loss of virus in washing steps.
Infections were synchronized by pre-adsorbing virus at 4$^{\circ}$C for 1h prior to initiation of infection by shifting temperature to 37$^{\circ}$C using pre-warmed media.
Cells were concurrently stained for HA and NS1 proteins at 10 hours after initiation of infection, and then analyzed by flow cytometry.
The level of HA protein was quantified in cells that were identified as infected based on being positive for NS1 protein (top), and the level of NS1 protein was quantified in cells that were identified as infected based on being positive for HA protein (bottom)
Synchronization resulted in a small decrease in variability in the levels of each viral protein, particularly in cells with intermediate levels.
But the effects were small compared to the overall variability in the protein levels, indicating timing of infection makes only a small contribution to the observed heterogeneity. 
Data are shown for three independent replicates.
}{\includegraphics[width=\linewidth]{figures/synchronize.jpg}}

\figsupp[Effects of infectious dose or coinfection state. \label{figsupp:flowdose}]
{
{\bf (A)}
Flow cytometry analysis of expression of viral proteins in cells infected at high (MOI 5 as calculated by TCID50 on MDCK-SIAT1 cells) or low (MOI 0.1) initial infectious dose.
Cells were concurrently stained for HA and NS1 proteins at 10 hours after initiation of infection, and then analyzed by flow cytometry.
The level of HA protein was quantified in cells that were identified as infected based on being positive for NS1 protein (left), and the level of NS1 protein was quantified in cells that were identified as infected based on being positive for HA protein (right)
While a higher dose leads to more cells expressing high amounts of viral protein, it does not greatly increase the amount of viral protein in either the low-expressing or high-expressing cells. 
Therefore, higher viral dose does not lead to a large continuous increase in viral protein production among all cells -- rather, it mostly changes the proportions of cells that fall in different parts of the highly heterogeneous distribution.
{\bf (B)}
Cells were co-infected with a mix of wild-type virus and pseudovirus in which the HA gene was replaced by GFP flanked by the terminal regions of the HA gene segment at an MOI of 0.1 for each virus. 
At 10 hours post-infection, cells were stained for NS1 and HA expression and analyzed by flow cytometry for these proteins and GFP.
Cells could be annotated as infected by virions of the same type (wild-type infection indicated by presence of HA, or pseudovirus infection indicated by the presence of GFP) or both types of virions (indicated by presence of HA and GFP).
Coinfected cells, like cells infected at a higher infectious dose, occupy different positions in the distribution of viral protein production but do not not exhibit a continuous increase in viral protein production.
Data are shown for three independent replicates.
}{\includegraphics[width=\linewidth]{figures/Coinf.jpg}}
\end{figure}

@@

\figsupp[Pre-treating to reduce oxidative stress decreases the fraction of infected cells expressing detectable viral protein. \label{figsupp:oxidative}]
{Cells were treated as indicated with 15 mM N-acetylcysteine (NAC), an antioxidant, and infected at an MOI of 0.1 as calculated by TCID50 on MDCK-SIAT1 cells. 
At 10 hours post-infection, cells were analyzed by flow cytometry for HA expression.
The percentage of HA-positive cells is indicated on the flow cytometry plots.
Data are shown for three independent replicates.
}{\includegraphics[width=0.7\linewidth]{figures/antiox.jpg}}
